Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-03-31 paper/paper.tex
add eyewriter

\subsection[short]{Apparatus}  % Do we want to change this to Equipment? 
% This may not need to be broken into subsections. Will decide before we resubmit. 
Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup. One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it. The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test.

@@

Typing Test MacBook Pro: The second MacBook Pro was used for the typing test. Since it did not have the eye tracker mounted on it, participants could easily access the keyboard and perform the typing test without any interference from the eye tracker.

Using two separate MacBook Pros allowed for the independent administration of the QBTest and typing test, ensuring that participants could perform each task without any physical hindrance from the eye tracker.

\subsubsection{EyeWriter 2.0}
\subsubsection{QB Test}
\subsubsection{Typing Test}
The typing program was written in Python and compiled using Python3.9. While python can run on any device that has python installed, this study only used Macbook Pros running on Sonoma or MacOS 14. The singularity of the devices was used as the center of the screen for the typing test was hard coded when setting the starting position of the window for the typing test.

>>>>

\subsection[short]{Apparatus}  % Do we want to change this to Equipment? 
% This may not need to be broken into subsections. Will decide before we resubmit. 
Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 1. One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it. The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test.

@@

Typing Test MacBook Pro: The second MacBook Pro was used for the typing test. Since it did not have the eye tracker mounted on it, participants could easily access the keyboard and perform the typing test without any interference from the eye tracker.
Using two separate MacBook Pros allowed for the independent administration of the QBTest and typing test, ensuring that participants could perform each task without any physical hindrance from the eye tracker.

\subsubsection{EyeWriter 2.0}
The IR camera captures the eye movements of the participant.
It is mounted on the laptop that participants use for the QBTest, allowing for the tracking of eye movements during the test.
IR LEDs are used to illuminate the eye to enhance the visibility of the eye for tracking purposes. 
These LEDs are also mounted on the laptop along with the IR camera. 
The mounting system holds the IR camera and IR LEDs in place relative to the participant's eye. 
It ensures that the camera has a clear view of the eye for accurate tracking. 
Cables are used to connect the IR camera and IR LEDs to the laptop. These cables transmit data and power between the components.
% \subsubsection{QB Test} 
\subsubsection{Typing Test}
The typing program was written in Python and compiled using Python3.9. While python can run on any device that has python installed, this study only used the two Macbook Pros. The singularity of the devices was used as the center of the screen for the typing test was hard coded when setting the starting position of the window for the typing test.
